Hydras \& Co.

### 2022-09-30 doc/chapter-encoding.tex
small changes

  The trick is to define a helper $h$ where
  $h\;n\;a$ is the natural number which represents
  the sequence $\langle \texttt{div2}(n-1),
  \texttt{div2}(n-2),\dots,\texttt{div2}\;1, \texttt{div2}\;0\rangle$.

@@

  The function \texttt{(evalStrongRec\;$n$\;$h$\;$c$)} computes
  $(f\;c)$ if $h$ is the helper associated with $f$.

@@

  This function is defined in
  \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair}.
   Definitions and related lemmas are quite tricky, but look easy to apply.

@@

>>>>

  The trick is to define a helper $h$ where
  $h\;n\;a$ is the natural number which encodes
  the sequence $\langle \texttt{div2}(n-1),
  \texttt{div2}(n-2),\dots,\texttt{div2}\;1, \texttt{div2}\;0\rangle$.

@@

  The function \texttt{(evalStrongRec\;$n$\;$h$\;$c$)} computes
  $(f\;c)$ if $h$ is the helper associated with $f$.
  This function is defined in
  \href{../theories/html/hydras.Ackermann.cPair.html}{Ackermann.cPair}.

@@

  Trying to compute the half of $5$ this way resulted in unbearably long computation times \dots.

   Definitions and related lemmas are quite tricky, but look easy to apply.

@@

  \index{ordinals}{Exercises}
    \begin{exercise}
      Prove formally that this implementation of \texttt{div2} is correct.
    \end{exercise}

   \index{ordinals}{Exercises}
    \begin{exercise}
     Define a function for computing the Fibonacci numbers by strong recursion.
    \end{exercise}
